---
title: "Group 17"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r setup, echo= FALSE, warning=FALSE, include = FALSE}
library(group17)
```
# Package Group 17

# Table of Contents

- [Introduction](#intro)
- [Get started](#start)
  - [Installation](#inst)
- [Methods](#methods)
  - [func1](#fun1)
  - [func2](#fun2)
  - [func3](#fun3)
  - [func4](#fun4)
  - [Plot occurence of Bases](#fun5)
- [Session Info](#session)
- [References](#ref)

# Introduction{#intro}

This package is builed around the central dogma of Molecular Biology, which describes the transfer of sequential information from DNA, RNA to Amino Acids (Crick, 1970).
With the package you are able to generate and translate DNA, RNA and Amino-Acid Sequences.
Further it enables you to perform basic statistic on those sequences.

# Get started{#start}

The R-package `group17` can be found on [Github](https://github.com/rforbiodatascience22/group_17_package).

## Installation{#inst}

To install `group17` from GitHub repository run the code below:
```{r eval = FALSE}
library(devtools)
# install package from github
devtools::install_github("rforbiodatascience22/group_17_package")
```

Load the library

```{r eval = FALSE}
library(group17)
```

# Methods{#methods}
## Function 1{#fun1} : F1_form_DNA
To create DNA sequence by random nucleotide selection following target length(size) use 'F1_form_DNA'
## Function 2{#fun2} : F2_transcribe
## Function 3{#fun3} : F3_get_codon
## Function 4{#fun4} : F4_translate
## Plot occurence of Bases{#fun5} : F5_plot_base_occurence
To plot the occurence of Bases in a DNA, RNA or Amino Acid Sequence use `plot_base_occurence()`


```{r, include = TRUE, fig.align='center'}
seq <- "ACGTCCCCGGGT"
plot_base_occurrence(sequence = seq)
```

## Session Info{#session}

```{r}
sessionInfo()
```


## References{#ref}

CRICK, F. Central Dogma of Molecular Biology. Nature 227, 561–563 (1970). https://doi.org/10.1038/227561a0

